Efficient pedigree recording for fast population genetics simulation

### 2018-01-11 forwards_paper.tex

\begin{figure}
    \begin{center}
        \includegraphics{sims/num_edges_50}
        \includegraphics{sims/simplify_timings}
    \end{center}
    \caption{
        \textbf{(A)}
        Number of edges in the simplified tree sequence
        for 50 Wright--Fisher simulations begun with no prior history,
        as a function of number of generations.
        Each line is one simulation, the black line gives the average,
        and the dotted line is the upper bound of equation \eqref{eqn:edge_bound}.
        \plr{Propose to add other figures as subfigures here; but better than this.}
        \textbf{(B)}
        Time required to simplify the first $k$ edges
        of \plr{what tree sequence?},
        plotted against $k$.
        \textbf{(C)}
        Time required to simplify
        \plr{what tree sequence?}
        down to a sample of size $n$,
        plotted against $n$
        (note the log scale;
        the time scales logarithmically with $n$).
        \label{fig:simplify_complexity}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{sims/simplify-results}
    \end{center}
    \caption{
        Time and space complexity of simplify.
        \textbf{(A)}
        Number of edges in the simplified tree sequence
        for 10 replicate Wright--Fisher simulations with $N=50$ as a function
        of number of generations.
        Each line is one simulation, the heavy blue line gives the average,
        and the dashed line is the upper bound of equation \eqref{eqn:edge_bound}.
        \textbf{(B)}
        Time required to simplify the first $k$ edges of a large (4.2GiB)
        unsimplified tree sequence produced by a forwards-time simulation plotted
        against $k$. The time scales linearly with the number of input edges.
        \textbf{(C)}
        Time required to simplify the tree sequence resulting from a coalescent
        simulation of 500K samples of a 200 megabase human chromosome
        for a random sample of $n$ samples, plotted against $n$
        (note the log scale; the time scales logarithmically with $n$).
        \label{fig:simplify_complexity}
    }
\end{figure}
